Performance Models for Data Transfers: A Case Study with Molecular Chemistry Kernels

### 2019-04-21 ICPP-19/communications.tex
Abstract Proofread

	%
	% The abstract is a short summary of the work to be presented in the article.
	\begin{abstract}
		%%		\todo[inline]{Initial submission deadline: April 15}
		%With increasing hardware complexity and systems with different memory nodes are ubiquitous in High Performance Computing (HPC). 
		In distributed memory systems, it is paramount to develop strategies to overlap the data transfers between memory nodes with the computation in order to exploit the full potential of these systems. In this paper, we consider the problem of determining the order of data transfers between two memory nodes for a set of independent tasks with the objective of minimizing the makespan. We prove that, with limited memory capacity, the problem of obtaining the optimal order of data transfers is NP-complete. We propose several heuristics to determine this order and discuss the conditions that might be favorable to different heuristics. We analyze our heuristics on traces obtained by running 2 molecular chemistry kernels, namely, Hartree–Fock (HF) and Coupled Cluster Single Double (CCSD) on 10 nodes of an HPC system. Our results show that some of our heuristics achieve significant overlap for moderate memory capacities and resulting in makespans that are very close to the lower bound.
	\end{abstract}

>>>>

	%
	% The abstract is a short summary of the work to be presented in the article.
	\begin{abstract}
		%%		\todo[inline]{Initial submission deadline: April 15}
		%With increasing hardware complexity and systems with different memory nodes are ubiquitous in High Performance Computing (HPC). 
		In distributed memory systems, it is paramount to develop strategies to overlap the data transfers between memory nodes with the computations in order to exploit the full potential of these systems. In this paper, we consider the problem of determining the order of data transfers between two memory nodes for a set of independent tasks with the objective of minimizing the makespan. We prove that, with limited memory capacity, the problem of obtaining the optimal order of data transfers is NP-complete. We propose several heuristics to determine this order and discuss the conditions that might be favorable to different heuristics. We analyze our heuristics on traces obtained by running 2 molecular chemistry kernels, namely, Hartree–Fock (HF) and Coupled Cluster Single Double (CCSD) on 10 nodes of an HPC system. Our results show that some of our heuristics achieve significant overlap for moderate memory capacities and resulting in makespans that are very close to the lower bound.
	\end{abstract}
